\documentclass[a4paper,12pt]{article}

%----------------------------------------------------------------------------------------
%	PACKAGES
%----------------------------------------------------------------------------------------
\usepackage{url}
\usepackage{parskip} 	
\usepackage{amssymb}

%other packages for formatting
\RequirePackage{color}
\RequirePackage{graphicx}
\usepackage[usenames,dvipsnames]{xcolor}
\usepackage[scale=0.9]{geometry}

%tabularx environment
\usepackage{tabularx}

%for lists within experience section
\usepackage{enumitem}

% centered version of 'X' col. type
\newcolumntype{C}{>{\centering\arraybackslash}X} 

%to prevent spillover of tabular into next pages
\usepackage{supertabular}
\usepackage{tabularx}
\newlength{\fullcollw}
\setlength{\fullcollw}{0.47\textwidth}

%custom \section
\usepackage{titlesec}				
\usepackage{multicol}
\usepackage{multirow}

%CV Sections inspired by: 
%http://stefano.italians.nl/archives/26
\titleformat{\section}{\Large\scshape\raggedright}{}{0em}{}[\titlerule]
\titlespacing{\section}{0pt}{10pt}{10pt}

%for publications
\usepackage[style=authoryear,sorting=ynt, maxbibnames=2]{biblatex}

%Setup hyperref package, and colours for links
\usepackage[unicode, draft=false]{hyperref}
\definecolor{linkcolour}{rgb}{0,0.2,0.6}
\hypersetup{colorlinks,breaklinks,urlcolor=linkcolour,linkcolor=linkcolour}
\addbibresource{citations.bib}
\setlength\bibitemsep{1em}

%for social icons
\usepackage{fontawesome5}

%debug page outer frames
%\usepackage{showframe}

%----------------------------------------------------------------------------------------
%	BEGIN DOCUMENT
%----------------------------------------------------------------------------------------
\begin{document}

% non-numbered pages
\pagestyle{empty} 

%----------------------------------------------------------------------------------------
%	TITLE
%----------------------------------------------------------------------------------------

% \begin{tabularx}{\linewidth}{ @{}X X@{} }
% \huge{Your Name}\vspace{2pt} & \hfill \emoji{incoming-envelope} email@email.com \\
% \raisebox{-0.05\height}\faGithub\ username \ | \
% \raisebox{-0.00\height}\faLinkedin\ username \ | \ \raisebox{-0.05\height}\faGlobe \ mysite.com  & \hfill \emoji{calling} number
% \end{tabularx}

\begin{tabularx}{\linewidth}{@{} C @{}}
\Huge{Akshat Sharma} \\[7.5pt]
\href{https://github.com/Screach37}{\raisebox{-0.05\height}\faGithub\ Screach37} \ $|$ \ 
\href{https://linkedin.com/in/sharmaakshat37}{\raisebox{-0.05\height}\faLinkedin\ sharmaakshat37} \ $|$ \ 
\href{https://screach37.github.io/Portfolio}{\raisebox{-0.05\height}\faGlobe \ screach37.github.io/Portfolio} \ $|$ \ 
\href{mailto:workakshat22@gmail.com}{\raisebox{-0.05\height}\faEnvelope \ workakshat22@gmail.com} \
\end{tabularx}

%----------------------------------------------------------------------------------------
%   Career Objective
%----------------------------------------------------------------------------------------
\section{Career Objective}
\begin{document}

Critical thinking DevOps Engineer and purpose-driven professional with capacity to be strong team \newline player plus work effectively independently with good written and verbal communication skills and a hard-working team player


%----------------------------------------------------------------------------------------
%	EDUCATION
%----------------------------------------------------------------------------------------
\section{Education}
\begin{tabularx}{\linewidth}{@{}l X@{}}
2020 - 2024 & B.Tech in \textbf{Computer Science} from SKIT, Jaipur \hfill (CGPA: 9.26) \\ 

2020 & CBSE Class 12th - Disha Delphi Public School \hfill  (87.8 \%) \\

2018 & CBSE Class 10th - Modern Sr. Sec. School \hfill  (89.6 \%) \\
\end{tabularx}

%----------------------------------------------------------------------------------------
% EXPERIENCE SECTIONS
%----------------------------------------------------------------------------------------

%Experience
\section{Work Experience}

\begin{tabularx}{\linewidth}{ @{}l r@{} }
\textbf{FAPL India} (Remote) & \hfill Nov, 2022\\[3.75pt]
\multicolumn{2}{@{}X@{}}{
\begin{minipage}[t]{\linewidth}
    \begin{itemize}[nosep,after=\strut, leftmargin=1em, itemsep=3pt]

        \item[--] Configured Custom Mail Server for FAPL India with over 100 users which helped reducing the overall cost by 61.1\%
        \item[--] Migrated mails from Zoho Mail to the custom mail server
        \item[--] Created using HMailServer on a Windows Server 2007
    \end{itemize}
    \end{minipage}
}
\end{tabularx}


%Professional Experience
\section{Experience}

\begin{tabularx}{\linewidth}{ @{}l r@{} }
% \textbf{Some Project} & \hfill \href{https://some-link.com}{Link to Demo} \\[3.75pt]
\multicolumn{2}{@{}X@{}}{
\begin{minipage}[t]{\linewidth}
    \begin{itemize}[nosep,after=\strut, leftmargin=1em, itemsep=3pt]
    
        \item[--] 2 + years of experience with \textbf{RedHat Linux} 7.x,8x, Debian 8.x and 9.x, CentOS 7.x and 8x, Oracle VM, VM-Ware, Ubuntu 18x,20x.
        
        \item[--] Experience in Designing, Installing and Implementing \textbf{Ansible} configuration management system and writing \textbf{playbooks for Ansible} and deploying applications.
        
        \item[--] Familiar with designing and deploying container-based production clusters using \textbf{Docker}.
        \item[--] Experienced with Docker container service, Creating \textbf{Dockerfiles, Docker Images and Containers}.
        
        \item[--] Automated a \textbf{CI/CD pipeline} for a Static Web App (Calculator) using \textbf{Travis CI, Docker and GitHub} (Available on Github under "Calculator" main branch and on Portfolio as well).
        
        \item[--] Working with Public Cloud Platform like \textbf{AWS}(Amazon Web Services) and good knowledge in using and managing various services like \textbf{AWS EC2, VPC, CLI, S3}, Create bucket and object. Worked with Amazon IAM console to create custom users and groups.
        
        \item[--] Administration and maintenance of application service like \textbf{DNS, Apache, SMTP, NFS, FTP and Samba} servers. Good understanding on client/server services like \textbf{NFS, HTTP/HTTPS, SSH, POP3/IMAP}.
        
        
        \item[--] Created a \textbf{Portfolio website} using \textbf{HTML, CSS, Bootstrap} and deployed it using \textbf{Github Actions}.
        
        \item[--] Created mini projects like Tic-Tac-Toe, ToDo List, Notes App using HTML, CSS and JS. 
    \end{itemize}
    \end{minipage}

}  \\
\end{tabularx}

%----------------------------------------------------------------------------------------
%	Positions Of Responsibility
%----------------------------------------------------------------------------------------


 \section{Positions Of Responsibility}
 \begin{itemize}[nosep,after=\strut, leftmargin=1em, itemsep=3pt]
        \item[--] \textbf{Coordinator} of \textbf{Tech-Innova Club}, SKIT.
        \item[--] Volunteered in a technical event ”Type-a-tack” in the College Fest, PRAVAH 2023.
        \item[--] Led a team of 6 for Smart India Hackathon - 2022 and got selected in the Prelims Round of SIH-2022.
    \end{itemize}

%----------------------------------------------------------------------------------------
%	SKILLS
%----------------------------------------------------------------------------------------
\section{Skills}
\begin{tabularx}{\linewidth}{@{}l X@{}}
Linux, Ansible, YAML, Docker, AWS, Azure, HTML, CSS, SaSS, Tailwind, Bootstrap, JS\\  
\end{tabularx}

%----------------------------------------------------------------------------------------
%	Accomplishments / Additional Details
%----------------------------------------------------------------------------------------
\section{Accomplishments / Additional Details}
\begin{tabularx}{\linewidth}{ @{}l r@{} }
\multicolumn{2}{@{}X@{}}{
\begin{minipage}[t]{\linewidth}
    \begin{itemize}[nosep,after=\strut, leftmargin=1em, itemsep=3pt]
        \item[--] \textbf{Certificate of achievement - LearnCodeOnline.in - Docker}
        \item[--]Issued: Jul 2022
        \item[--] Certificate ID: https://courses.learncodeonline.in/learn/certificate/6626356-49488
        
        \item[--] \textbf{Certificate for Completion of Linux Training - Spoken Tutorial IIT Bombay}
        \item[--] Issued: May 2022
        \item[--] Certificate ID: - 2976599Y71
        
        \item[--] \textbf{Certificate for Completion of Cpp Training - Spoken Tutorial IIT Bombay}
        \item[--] Issued: Jan 2022
        \item[--] Certificate ID: - 29765998QZ

        \item[--] \textbf{Certificate of Distinction in Cambridge ESOL Examination} Starters, Flyers, KET (Key English Test) and PET (Preliminary English Test).
        
        \item[--] \textbf{Certificate of Distinction} in Grade3, Grade 5 and Grade 6 of \textbf{Trinity College London}.

    \end{itemize}
    \end{minipage}
}
\end{tabularx}

%----------------------------------------------------------------------------------------
%	Interests
%----------------------------------------------------------------------------------------

\section{Interests}
\begin{tabularx}{\linewidth}{ @{}l r@{} }
\multicolumn{2}{@{}X@{}}{
Playing Cricket and Badminton, Listening Music, Writing Songs, E-Sports
}\end{tabularx}

\end{document}